Methodology for Assessing the State of the Practice for Domain X

### 2020-09-09 StateOfPractice/Methodology/Methodology.tex
updated Emprirical Measures section of Methodology

\subsection{Raw Data}
Measures that can be extracted from on-line repos.

\subsection{Processed Data}
Metrics that can be calculated from the raw data.

\subsection{Tool Tests}
\ad{This section is currently a note of unorganized contents. Most parts will beremoved or relocated.}

@@

\subsubsection{git-stats}\label{scc}
\href{https://github.com/boyter/scc}{GitHub repo}

@@

@@

\subsubsection{git-stats}\label{scc}
\href{https://github.com/boyter/scc}{GitHub repo}

>>>>

\subsection{Raw Data}
The following raw data measures are extracted from repositories:

\begin{itemize}
\item Number of stars.
\item Number of forks.
\item Number of people watching the repository.
\item Number of open pull requests.
\item Number of closed pull requests.	
\item Number of developers.	
\item Number of open issues.
\item Number of closed issues.
\item Initial release date.
\item Last commit date.
\item Programming languages used.
\item Number of text-based files.
\item Number of total lines in text-based files.
\item Number of code lines in text-based files.
\item Number of comment lines in text-based files.
\item Number of blank lines in text-based files.
\item Number of binary files.  
\item Number of total lines added to text-based files.
\item Number of total lines deleted from text-based files.
\item Number of total commits.
\item Numbers of commits by year in the last 5 years. (Count from as early as possible if the project is younger than 5 years.) 
\item Numbers of commits by month in the last 12 months.
\end{itemize}

\subsection{Processed Data}
The following measures are calculated from the raw data:

\begin{itemize}
\item Status of software package (dead or alive).
\item Percentage of identified issues that are closed.
\item Percentage of code that is comments.
\end{itemize}

\subsection{Tool Tests}
The following tools are used to gather some of the raw data from the repositories:

@@

\subsubsection{scc}\label{scc}
\href{https://github.com/boyter/scc}{GitHub repo}

@@

\subsubsection{git-stats}
\href{https://github.com/tomgi/git_stats}{GitHub repo}

@@

\subsubsection{scc}
\href{https://github.com/boyter/scc}{GitHub repo}
